Background Subtraction via Deep Variation Transformation

### 2018-08-16 draft.tex
revised the abstract

\begin{abstract}
%
Previous work analyzes the variation of pixels for background subtraction which is generally considered as the binary classification of pixels in time sequence.
%
In this paper, we focus on transforming the variation into another space where the pixels are easier classified,
with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
%
In the DPVTL model,
the variation is represented by the sequence of pixels' observations and used as the input of the fully convolutional network.
%
The fully convolutional network is trained to learn the pattern of variation for transformation with the output leaded by grounthtruth data.
% XXX 这句话还是有点问题
Benefied from the ingenious utilization of FCN leading by our clear congnition of essence about background subtractoin problem,
proposed approached adaptively generate superior peroformances in diversly complex scenes.
%
Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
%
% We also put
% forward a novel background subtraction framework called the
% Integration of Foreground and Background (IFB) cues.
% % a video stream. 
% %之前方法 下一句用的focus on加ing，这就用ed，形成对比
% % Previous works generally proposed the artificial model with the utilization of lowlevel or hand-crafted features to analyze the variation of pixels' observation.
% Previous work generally analyze the variation of pixels' observation with the u/cygdrive/c/Users/Ray/Downloads/3.iebktilization of hand-crafted features.
%     %in time sequence.
% % 为什么之前方法会失败
% However, due to the complexity and diversity of nature,
% the variation of observations becomes so hard to classify by hand-crafted features.
%     %in complexly natural scenes.
% %我们的改进
% In this paper, we focus on transforming the obserations sequence into another easier classfied space,
% and a novel background subtraction method based on Deep Variation Transformation (DVT) is proposed.
% % XXX 为什么是networks，不是network呢？
% In the DVT model,
% the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
% %
% In particlar, 
% a the variation of observation represented by pixel sequence is reshaped into a image patch as the input of FCN network.
% %
% Then, the output of network is classfied and reverted to the corresponding sequence for the binary classfication of oberservations' variation.
% %
% Benefied from the ingenious utilization of FCN network leading by our clear congnition of essence about background subtractoin problem,
% proposed approached adaptively generate superior peroformances in diversly complex scenes.
% %
% Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
% 
% 
% 
% videos are divided into fixed length image stacks by temporal sampling. 
%     Next, image stacks is broken down into pixel observation matrixes as the input of the FCN to learn the patterns of pixel variation. 
%     Each of the pixel matrixes contains a piece of temporal information about pixel variation over a period of time.  
% The architecture of our FCN is devised from the semantic segmentation problem. 
% %效果
% Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ observations. 
%     Compared with some state-of-the-art methods, both deep learning and traditional methods, the proposed approach outperform its conventional counterparts significantly owing to the utilizing of temporal information.
\end{abstract}

>>>>

\begin{abstract}
%
Previous approaches to background subtraction generally analyzes the variation of pixels' observation.
%for background subtraction.
%
%Background subtraction is generally considered as the binary classification of pixels' observations in time sequence,
%and preivous work 
%
%Previous work analyzes the variation of pixels for background subtraction which is generally considered as the binary classification of pixels in time sequence.
%
%
In this paper, we focus on transforming the variation into a new space where that there is an obvious difference between the patterns of variation produced by the moving objects and the background,
and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
%
% 
%     
%     
%     another space where the observations of pixels are easier classified,
% with the motivation to  that there is difference between the patterns of variation produced by the moving objects and the background.
% %
% We also put forward a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
% %
% with the consideration that the observations of pixels are usually so hard to analyze due to the unpredictability and complexity of natural scenes,
%and a novel background subtraction method called Deep Pixel Variation Transformation Learning (DPVTL) is proposed.
%
In particular,
the variation is represented by the sequence of pixels' observations and used as the input of the fully convolutional network.
%
Then, the fully convolutional network is trained to learn the pattern of variation for the transformation followed by a liner classifier for labeling the pixels as foreground or background.
%    with the supervision leaded by grounthtruth data.
% XXX 这句话还是有点问题
Benefied from the ingenious utilization of deep learning network leading by our clear congnition of essence about background subtractoin problem,
proposed approached adaptively generate superior peroformances in diversly complex scenes.
%
Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
%
% We also put
% forward a novel background subtraction framework called the
% Integration of Foreground and Background (IFB) cues.
% % a video stream. 
% %之前方法 下一句用的focus on加ing，这就用ed，形成对比
% % Previous works generally proposed the artificial model with the utilization of lowlevel or hand-crafted features to analyze the variation of pixels' observation.
% Previous work generally analyze the variation of pixels' observation with the u/cygdrive/c/Users/Ray/Downloads/3.iebktilization of hand-crafted features.
%     %in time sequence.
% % 为什么之前方法会失败
% However, due to the complexity and diversity of nature,
% the variation of observations becomes so hard to classify by hand-crafted features.
%     %in complexly natural scenes.
% %我们的改进
% In this paper, we focus on transforming the obserations sequence into another easier classfied space,
% and a novel background subtraction method based on Deep Variation Transformation (DVT) is proposed.
% % XXX 为什么是networks，不是network呢？
% In the DVT model,
% the fully convolutional network (FCN) is untlized to transform the sequence of pixels' observations into a new representation of pixels' observations with more obvious features for classfication.
% %
% In particlar, 
% a the variation of observation represented by pixel sequence is reshaped into a image patch as the input of FCN network.
% %
% Then, the output of network is classfied and reverted to the corresponding sequence for the binary classfication of oberservations' variation.
% %
% Benefied from the ingenious utilization of FCN network leading by our clear congnition of essence about background subtractoin problem,
% proposed approached adaptively generate superior peroformances in diversly complex scenes.
% %
% Comprehensive experiments in standard benchmarks demonstrate the superiority of proposed approach compared with state-of-the-art methods including both deep learning and traditional methods.
% 
% 
% 
% videos are divided into fixed length image stacks by temporal sampling. 
%     Next, image stacks is broken down into pixel observation matrixes as the input of the FCN to learn the patterns of pixel variation. 
%     Each of the pixel matrixes contains a piece of temporal information about pixel variation over a period of time.  
% The architecture of our FCN is devised from the semantic segmentation problem. 
% %效果
% Experiment shows that our model has a strong learning ability to the patterns of those permutations of pixels’ observations. 
%     Compared with some state-of-the-art methods, both deep learning and traditional methods, the proposed approach outperform its conventional counterparts significantly owing to the utilizing of temporal information.
\end{abstract}
